Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-02 ms.tex
fixed the UT times in the table, SpecMatch-Emp fix and rearranged figures.

\begin{deluxetable}{cccccccc}
\tablecaption{List of Spectroscopic Observations}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
\end{deluxetable}

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Median spectrum of \shStar\ \citep{} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}

@@

\subsection{Specmatch}\label{sec:SpecMatch}

We also use the open-source \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{specmatch} grid of $R=55,000$, so we do not convolve the input data for \texttt{specmatch}.
We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.

Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
The effective temperature and radius parameters show clear global $\chi^2$ minima for the HIRES spectral libraries.
However, the metallicity is less well constrained.
The resulting best-fit parameters from \texttt{specmatch} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
The output \texttt{specmatch} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
Figure \ref{fig:specMatchComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{specmatch}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.
The effective temperature and radii show clear global minima.}\label{fig:specMatch}
\end{centering}
\end{figure*}

We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
A brighter transiting disintegrating system may reveal itself more strongly, if discovered in the TESS field.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatchComb}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Right) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
\caption{(Left) Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.
(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
\end{centering}
\end{figure*}

@@

\software{astropy \citep{astropy2013}, 
	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
	\texttt{iraf},
	\texttt{specmatch} tool \citep{yee2017specMatch} 
          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
          }

>>>>

\begin{deluxetable}{cccccccc}
\tablecaption{List of Spectroscopic Observations}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 & 2013 Jun 22 & 12:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 & 2013 Jun 22 & 13:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 05:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 06:19 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 07:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 08:15 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 09:17 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 05:34 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 06:17 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 07:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 08:31 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 09:14 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
\end{deluxetable}

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Median spectrum of \shStar\ \citep{masuda2018rvKIC1255} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}

@@

\subsection{SpecMatch-Emp}\label{sec:SpecMatch-Emp}

We also use the open-source \texttt{SpecMatch-Emp} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
\texttt{SpecMatch-Emp} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
%The median spectrum from 2015 has a resolution of $R=60,000$, which is close to the \texttt{SpecMatch-Emp} grid of $R=55,000$, so we do not convolve the input data for \texttt{SpecMatch-Emp}.
We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.

Figure \ref{fig:SpecMatch-Emp} shows the chi-squared differences between the median Subaru spectrum and the models.
The effective temperature and radius parameters show clear global $\chi^2$ minima for the HIRES spectral libraries.
However, the metallicity is less well constrained.
The resulting best-fit parameters from \texttt{SpecMatch-Emp} are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$ and Mass=0.7 $\pm 0.1 $M$_\odot$.
The output \texttt{SpecMatch-Emp} age constraint of 9.6 $\pm$ 0.2 Gyr is likely an underestimated error in the age.
Figure \ref{fig:SpecMatch-EmpComb} shows the linear combination of spectra that best-fit \shStar\ from \texttt{SpecMatch-Emp}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
\caption{$\chi^2$ as a function of stellar parameters found by \texttt{SpecMatch-Emp}.
The effective temperature and radii show clear global minima.}\label{fig:SpecMatch-Emp}
\end{centering}
\end{figure*}

We summarize these \texttt{SpecMatch-Emp} and BOSZ results in Table \ref{tab:stellObsParams}, which both favor a main-sequence log(g) $\approx$ 4.6 star.
Our analysis of the median 2015 spectrum therefore indicates that the stellar spectrum shows no strong contamination from planet disintegration activity.
Unfortunately, this makes diagnosing the gaseous material evaporating from sublimated dust grains challenging to detect.
A brighter transiting disintegrating system may reveal itself more strongly, if discovered in the TESS field.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:SpecMatch-EmpComb}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
(Right) The residuals show significant deviations near phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Right) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}
Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
\caption{(Left) Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
\end{centering}
\end{figure*}

@@

\software{astropy \citep{astropy2013}, 
	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
	\texttt{iraf},
	\texttt{SpecMatch-Emp} \citep{yee2017specMatch} 
          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
          }
